---
title: '"AY22-2 SE370: Lesson 24 Exploratory Data Analysis'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyr)
library(dplyr)
```

## Exploratory Data Analysis

What is EDA?

-   *Type your definition here...*

## Let's do some EDA...

```{r }

```

#### Answer these questions about your data:

1.  What does each row represent?

    ANS:

2.  How many rows do you have?

    ANS:

3.  Are there missing values in your data? How are they coded?

    ANS:

#### Clean your data:

1.  Replace all missing values with `NA`. *Hint*: Take all things called "blank" and replace them with `NA`

    ```{r}

    ```

2.  Convert columns that should be numeric...to numeric. *Hint: use the mutate_at() function to mutate a bunch of columns at one time.*

    ```{r}

    ```

3.  Recode the `HIGHDEG` column so that '4' = 'bachelors', '3' = 'associates', '2' and '1' = 'vocational', '0' = 'non-degree'. *Hints: use mutate and recode together; `HIGHDEG` must start as a character for recode to work.*

    ```{r}

    ```

#### Answer the following questions:

1.  What are the top 5 schools with the highest in-state tuition?

    ```{r}

    ```

2.  What are the top 5 schools with the lowest in-state tuition?

    ```{r}

    ```

3.  Count and plot the types of accreditation?

    ```{r}

    ```

4.  Is there a relationship between `SAT_AVG` and Admissions Rate? Answer with a plot.

    ```{r}

    ```

#### Extra questions (you don't need to answer these...only for fun!)

1.  Is there a relationship between faculty salary and tuition?

    ```{r}

    ```

2.  Create facet plots showing the distributions (densities) of SAT scores by degree type?

    ```{r}

    ```

3.  Are entry ages the same for all degree types? Show with a boxplot.

    ```{r}

    ```

4.  Create a stacked barplot showing the share of men and women for the 10 most expensive out of state tuition.

    ```{r}

    ```
